### 2016-11-21 report/survey.tex
Added one platform and expanded explanation.
Added the bib file. Still need to make auto-generation of results,
and the same for hardware information and other stuff.

\begin{tabular}{l|r|r}
 & PowerGraph & OpenG \\ \hline
BFS & $87.4$ & $341$ \\ \hline
SSSP & $1.09$ & $3.08$ \\ \hline
\end{tabular}

The

>>>>

\begin{tabular}{l|r|r|}
 & PowerGraph & OpenG \\ \hline
BFS & $87.4$ & $341$ \\ \hline
SSSP & $1.09$ & $3.08$ \\ \hline
\end{tabular}

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}. Here, ``|'' means ``or'' and ``+'' means ``and.'' FOSS means Free and Open Source Software. The quotes around ``yes'' for HPC mean that the product claims to be amenable to high performance computing. Whether these actually achieve their goal is one of the purposes of this project.
\begin{savenotes}
	\begin{table}[htb]
		\centering
		% \small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			every head row/.style={after row=\midrule},
			columns/Name/.style={string type, column type={l|}},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
			columns/Target/.style={string type},
			columns/FOSS/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=
					\ifx&##1&% Only make a footnote if the cell is nonempty
						##1
					\else
						\footnote{##1}
					\fi}
			},
		]{platforms.csv}
	\end{table}
\end{savenotes}

\bibliographystyle{acm}
\bibliography{drp}
